\Large \bf On semidefinite-representable sets over valued fields

### 2025-10-10 article/paper_padic_spec.tex
Correction de quelques typos.

In this paper we consider the situation where input data are defined over fields $K$ with a prescribed valuation map $\val$ on $K$. In this context a polyhedron is defined as a set of vectors such that some linear forms have nonnegative or infinite vluation ({\it cf.} \Cref{def_polyhedra}). The prototype of valued field we target is the field of $p$-adic numbers with $p$-adic valuation.
%%%\todo{Give motivations for p-adic precision of LP/SDP.}
Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral} and tropical methods applied to non-archimedean semidefinite programming \cite{allamigeon2016solving,allamigeon_tropical_2020}.

@@

Throughout the paper, $(K,\val)$ refers to a complete valued field, namely $K$ is a field
and $\val : K \twoheadrightarrow \Gamma \cup \{+\infty\}$ is a valuation on $K$, $\Gamma$ an
ordered abelian group. The valuation is often assumed to be discrete ({\it i.e.} $\Gamma=\ZZ$)
with $\pi \in K$ a uniformizer. The ring of integers of $K$ is
$$
\OK = \{x \in K : \val(x) \geq 0\},
$$
$\kappa = \OK/\mathfrak{m}_K$ its residue field, with
$\mathfrak{m}_K = \{x \in K : \val(x) > 0\}$.
For $k \in \N$, we write $O(\pi^k)$ for $\pi^k \OK$.
A typical example of $K$ as above is the field of $p$-adic numbers 
$\QQ_p$ equipped with the $p$-adic valuation. For this example, we 
have $\OK = \ZZ_p$. Another example is the field of Laurent series
$K=\QQ(\!(t)\!)$ equiped with $t$-adic valuation,
in which case $\OK = \QQ \llbracket t \rrbracket$.
We refer to \cite{Serre:1979,engler2005valued} for a
general introduction to such fields
and to \cite{caruso_computations_2017}
for an introduction to effective computations over $p$-adic numbers.

The $K$-vector space of polynomials of degree $\leq d$ on $x=(x_1,\ldots,x_n)$
with coefficients in $K$ is denoted by $K[x]_{d}$. The ring of matrices of
size $p \times q$ with entries in a ring $R$ is $R^{p \times q}$ and the general
linear group in $R^{n \times n}$ is $\GL_n(R)$.
For the sake of ease of writing, block-diagonal matrices with blocks
$B_1,\ldots,B_d$ are denoted by $\diag(B_1, \ldots, B_d)$, the null matrix of
size $p \times q$ by ${\bf 0}_{p,q}$, and the identity matrix by $I_t$.

@@

\begin{example}
  The \emph{closed unit ball} $\OK^n=B_\infty(K^n)$ in $K^n$ for the supremum norm $||\cdot||_{\infty}$ is the
  polyhedron defined as the set of $x=(x_1,\ldots,x_n) \in K^n$ such that $||x||_{\infty} =
  \max_i\{x_i\} \leq 1$, in other words, such that $\val(x_i) \geq 0$, for all $i=1, \ldots, n$.
  In other words, $\OK^n$ is the polyhedron in $K^n$ defined by the affine polynomials
  $\ell_i(x)=x_i$, $i=1,\ldots, n$, and $e=0$. %%%%%(its affine hull is indeed the whole $K^n$).
\end{example}

@@

\begin{lemma}[DI${}_{proj}$]
Let $f : K^n \to K^n, \: (x_1,\dots,x_{n-1},x_n) \mapsto (x_1,\dots,x_{n-1})$ and $\PP$ a polyhedron in $K^n$ defined only by inequalities. 
Then $f(\PP)$ is a polyhedron defined only by inequalities. \label{lem:DIproj}
\end{lemma}
\begin{proof}
We assume that $\PP \neq \emptyset$.
Let us write the conditions defining $\PP$
in matrix form:
$\val(A X+B) \geq 0$ 
with $A \in M_{q,n}(K)$, $B \in K^q$
and $X=(x_1,\dots,x_n)^\intercal$.

@@

Let $\Qc= P(\PP)$
We now prove that $\Delta (\Qc)$ is a polyhedron.
One can write that $\Delta$ is the composition
of the immersion 
$K^r \rightarrow K^n$
$(x_1,\dots,x_r)\mapsto (x_1,\dots,x_r,0,\dots,0),$ 
 the diagonal invertible mapping
$K^l \rightarrow K^l$,
$(x_1,\dots,x_r)\mapsto (\delta_1,\dots,\delta_r x_r)$,
and the projections
$(x_1,\dots,x_{r+1})\mapsto (x_1,\dots,x_{r}),$
 $(x_1,\dots,x_{r+2})\mapsto (x_1,\dots,x_{r+1}),$
 $\dots,$
 $(x_1,\dots,x_{n})\mapsto (x_1,\dots,x_{n-1}).$
 Thus, thanks to Lemmas \ref{lem:DIimm} DI${}_{imm}$, \ref{lem:DIproj} DI${}_{proj}$ and \ref{lem:DIaut} DI${}_{aut}$, $\Delta (\Qc)$ is a polyhedron.
 One can note that it is only when applying the immersion as the last mapping in the composition chain that equalities are needed to define the last polyhedron.

@@

\begin{proof}
    Let $\PP$ be such polyhedron. We assume that $\PP \neq \emptyset$. By \ref{prop:carac} there exist a polydisc $D = \{x \in K^n : \val s_i x_i - b_i \ge 0, i=1,\ldots,n \}$ for some $s_1,\ldots,s_n, b_1,\ldots,b_n \in K ^n$ and an affine map $f : K^n \to K$ such that $\PP = f(D)$. Let $a_0,a_1,\ldots,a_n \in K$ such that $f(x) = a_0 + a_1 x_1 + \ldots + a_n x_n$. We can assume, with no loss of generality, that the $a_i$'s are nonzero.

@@

\begin{theorem} \Cref{algo_LP} is correct.
\end{theorem}
\begin{proof}
  If the linear system $Dx=e$, Problem \eqref{LP} is infeasible
  and \Cref{algo_LP} outputs correct answer at step \ref{step:linear_empty}.
  Else, by \Cref{reducD} the input problem can be reduced to a new linear
  program with $D={\bf 0}$ and $e=0$, which is done at steps
  \ref{step:reducD:begin}-\ref{step:reducD:end},
  and the correct recursion is given at step \ref{step:reducD}.
  The reduction based on SNF from \Cref{solsLP} is performed at
  steps \ref{step:solsLP:begin}-\ref{step:solsLP:end} and the output
  at step \ref{step:solsLP} is correct.

@@

Recall that the \emph{Newton polygon} of a polynomial $P = \sum_{i=0}^{d} a_i T^i \in K[T]$ is
defined as the inferior convex hull of the set $\{(i, \val a_i) \,|\, 0 \le i \le d\}$, {\it i.e.} the
graph of the greatest convex function $\PP : [0,d] \to \R$ such that $\PP(i) \leq \val a_i$
for $i=1,\ldots,d$. This function is piecewise affine and its slopes are exactly the opposites of the valuations
of the roots of $P$.

The following result shows that testing positive semidefiniteness of matrices over
valued fields reduces to checking whether the coefficients of $\chi_M$ are integers.

@@

As a consequence, matrices with integer coefficients are positive semidefinite.

@@

\begin{example}
  Let
  $$
  M = \begin{bmatrix} \frac{3}{5}+5 & \frac{4}{5} \\ \frac{4}{5} & -\frac{3}{5} \end{bmatrix}.
  $$
  The characteristic polynomial of $M$
  is $\chi_M = T^2-5T-4$. However when seen as a matrix over $K=\mathbb{Q}_5$, then $\chi_M \in \mathbb{Z}_5[T] = \OK[T]$: then $M \in (\mathbb{Q}_5)^{2 \times 2}_+$, nevertheless $M \not\in (\mathbb{Z}_5)^{2\times 2}$, hence
  $(\mathbb{Q}_5)^{2 \times 2}_+ \not\subset (\mathbb{Z}_5)^{2 \times 2}$.
\end{example}

@@

In the real case, one often abuses of the definition of spectrahedra, saying that the set
$\{x \in \mathbb{R}^n : A_0+\sum_{i=1}^n x_iA_i \succeq 0\}$ is also a spectrahedron.
Remark that this also yields that every affine subset of $\mathbb{R}^n$ is also
a spectrahedron: indeed an affine equation $\ell(x) = 0$ is equivalent to the two inequalities
$\ell(x) \geq 0 \leq -\ell(x)$. Over a valued field it is necessary to give the following
definition in order to include affine sets in the family of spectrahedra.

@@

The class of spectrahedra in $K^{d \times d}$ (or in $K^n$) is closed under intersection: indeed one
has $(\mathcal{L}_1 \cap K^{d \times d}_+) \cap (\mathcal{L}_2 \cap K^{d \times d}_+) =
(\mathcal{L}_1 \cap \mathcal{L}_2) \cap K^{d \times d}_+$
, for two affine spaces
$\mathcal{L}_1 = A_0+\span{A_1,\ldots,A_n}$ and $\mathcal{L}_2 = A_0+\span{B_1,\ldots,B_n}$,
and
$(L_1 \cap \mathcal{S}_A) \cap (L_2 \cap S_B) = (L_1\cap L_2) \cap S_{\diag(A,B)}$ for
two affine spaces $L_1,L_2 \subset K^n$.
Moreover this class contains polyhedra in $K^n$.

@@

\begin{definition}[Polyannulus]\label{def_annuli}
  A set of the form $\mathcal{C} = \{x \in K \,|\, a \le \val(x) \le b\}$, for $a,b \in \R^*_+$,
  is called \emph{annulus}. A product $\mathcal{C}_1 \times \mathcal{C}_2 \times \cdots \times \mathcal{C}_n \subset K^n$,
  where each $C_i \subset K$ is an annulus, is called a \emph{polyannulus}.
\end{definition}

@@

\begin{theorem}
Polyannuli in $K^n$ are spectrahedral shadows with height $m=n$ and degree $d=4n$.
\end{theorem}
\begin{proof}
  Let $\mathcal{C} = \mathcal{C}_1 \times \cdots \times \mathcal{C}_n \subset K^n$ be as in \Cref{def_annuli},
  for some annuli $\mathcal{C}_1,\ldots,\mathcal{C}_n \subset K$. We claim that each $\mathcal{C}_i$ is a spectrahedral
  shadow of height $1$ and degree $4$. Assume $\mathcal{C}_i = \{x_i \in K : a_i \leq \val(x_i) \leq b_i\}$
  for some $a_i, b_i \in \R^*_+$ with $a_i < b_i$. Consider the spectrahedron
  $\mathcal{S}_{M^{(i)}} \subset K^2$ defined by
  $$
  \mathcal{S}_{M^{(i)}} = \left\{(x_i,y_i) \in K^2 :
  M^{(i)}(x_i,y_i) := \diag\left(\pi^a x_i, \pi^{-b} y_i,
  \begin{bmatrix}
    \pi^{-1} & -\pi^{-1} x_i  \\
    \pi^{-1} y_i & - \pi^{-1} \\
  \end{bmatrix}\right) \succeq 0
  \right\}.
  $$
  We claim that $x_i \in \mathcal{C}_i$ if and only if there exists $y_i \in K$ such that $(x_i,y_i) \in
  \mathcal{S}_{M^{(i)}}$.
  Indeed, by \Cref{caracsdp}, $M^{(i)}(x_i,y_i) \succeq 0$ if and only if $(x_i,y_i)$ is a solution of the system
  of inequalities:
  \begin{equation}
    \label[type]{eq:annulussyst}
    \begin{cases}
      \val(\pi^a x_i) \ge 0 \\
  \val(\pi^{-b} y_i) \ge 0\\
  \val(\pi^{-1}- \pi^{-1}) = +\infty \ge 0\\
  \val(\pi^{-2}\left( x_iy_i-1 \right))  \ge 0 
\end{cases}
\iff	
\begin{cases} 
  \val\left(x_i\right)\ge a\\
  \val\left(y_i\right)\ge -b\\
  \val\left(x_iy_i-1 \right) \ge 2
\end{cases}
\end{equation} 
  %Therefore, if $(x, y)$ verifies \eqref{eq:annulussyst} then $\val\left(x\right)\ge a$, $\val\left(y\right)\ge -b$ and $ \left( xy-1 \right) \ge 2$.
  The last inequality implies that $\val\left(x_i\right)+\val\left(y_i\right)=\val\left(x_iy_i\right) = \val\left(-1\right) =0$ and therefore that $\val\left(x_i\right)=-\val\left(y_i\right)\le -(-b) = b$, so $x_i \in \mathcal{C}_i$. 
Reciprocally if $x_i \in \mathcal{C}_i$ then $(x_i,x_i^{-1})$ is a solution of \eqref{eq:annulussyst}.
This proves our claim.
Finally, since $\mathcal{C} = \mathcal{C}_1 \times \cdots \times \mathcal{C}_n$, one has
\begin{equation*}
  \begin{aligned}
    \mathcal{C} &=
    \{x=(x_1,\ldots,x_n) \in K^n : \exists y = (y_1,\ldots,y_n) \in K^n, (x_i,y_i) \in
    \mathcal{S}_{M^{(i)}}, i=1,\ldots,n\} \\
    &= \{x \in K^n : \exists y \in K^n, (x,y) \in \mathcal{S}_M\}
  \end{aligned}
\end{equation*}
with $\mathcal{S}_M = \diag\left(M^{(1)}, M^{(2)}, \ldots, M^{(n)}\right) \in K[x,y]^{4n \times 4n}.$
\end{proof}

We conclude proving that, in general, annuli are not spectrahedral.

>>>>

In this paper we consider the situation where input data are defined over fields $K$ with a prescribed valuation map $\val$ on $K$. In this context a polyhedron is defined as a set of vectors such that some linear forms have nonnegative or infinite valuation ({\it cf.} \Cref{def_polyhedra}). The prototype of valued field we target is the field of $p$-adic numbers with $p$-adic valuation.
%%%\todo{Give motivations for p-adic precision of LP/SDP.}
Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral} and tropical methods applied to non-archimedean semidefinite programming \cite{allamigeon2016solving,allamigeon_tropical_2020}.

@@

Throughout the paper, $(K,\val)$ refers to a complete valued field, namely $K$ is a field
and $\val : K \twoheadrightarrow \Gamma \cup \{+\infty\}$ is a valuation on $K$, $\Gamma$ an
ordered abelian group. The valuation is often assumed to be discrete ({\it i.e.} $\Gamma=\ZZ$)
with $\pi \in K$ a uniformizer. The valuation ring of $K$ is
$$
\OK = \{x \in K : \val(x) \geq 0\},
$$
$\kappa = \OK/\mathfrak{m}_K$ its residue field, with
$\mathfrak{m}_K = \{x \in K : \val(x) > 0\}$. An element of $\OK$ is called integral (at $\val$).
For $k \in \N$, we write $O(\pi^k)$ for $\pi^k \OK$.
A typical example of $K$ as above is the field of $p$-adic numbers 
$\QQ_p$ equipped with the $p$-adic valuation. For this example, we 
have $\OK = \ZZ_p$. Another example is the field of Laurent series
$K=\QQ(\!(t)\!)$ equiped with $t$-adic valuation,
in which case $\OK = \QQ \llbracket t \rrbracket$.
We refer to \cite{Serre:1979,engler2005valued} for a
general introduction to such fields
and to \cite{caruso_computations_2017}
for an introduction to effective computations over $p$-adic numbers.

The $K$-vector space of polynomials of degree $\leq d$ on $x=(x_1,\ldots,x_n)$
with coefficients in $K$ is denoted by $K[x]_{d}$. The ring of matrices of
size $p \times q$ with entries in a ring $R$ is $R^{p \times q}$ and the general
linear group in $R^{n \times n}$ is $\GL_n(R)$.
For the sake of ease of writing, block-diagonal matrices with blocks
$B_1,\ldots,B_d$ are denoted by $\diag(B_1, \ldots, B_d)$, the null matrix of
size $p \times q$ by ${\bf 0}_{p,q}$, and the identity matrix of size $t \times t$ by $I_t$.

@@

\begin{example}
  The \emph{closed unit ball} $\OK^n=B_\infty(K^n)$ in $K^n$ for the supremum norm $||\cdot||_{\infty}$ is the
  polyhedron defined as the set of $x=(x_1,\ldots,x_n) \in K^n$ such that $||x||_{\infty} =
  \max_i\{\vert x_i \vert\} \leq 1$, in other words, such that $\val(x_i) \geq 0$, for all $i=1, \ldots, n$.
  As such, $\OK^n$ is the polyhedron in $K^n$ defined by the affine polynomials
  $\ell_i(x)=x_i$, $i=1,\ldots, n$, and $e=0$. %%%%%(its affine hull is indeed the whole $K^n$).
\end{example}

@@

\begin{lemma}[DI${}_{proj}$]
Let $f : K^n \to K^{n-1}, \: (x_1,\dots,x_{n-1},x_n) \mapsto (x_1,\dots,x_{n-1})$ and $\PP$ a polyhedron in $K^n$ defined only by inequalities. 
Then $f(\PP)$ is a polyhedron defined only by inequalities. \label{lem:DIproj}
\end{lemma}
\begin{proof}
We assume that $\PP \neq \emptyset$.
Let us write the conditions defining $\PP$
in matrix form:
$\val(A X+B) \geq 0$ 
with $A \in M_{q,n}(K)$, $B \in K^q$
and $X=(x_1,\dots,x_n)^\intercal$.

@@

Let $\Qc= P(\PP)$
We now prove that $\Delta (\Qc)$ is a polyhedron.
One can write that $\Delta$ is the composition
of the immersion 
$K^r \rightarrow K^n$
$(x_1,\dots,x_r)\mapsto (x_1,\dots,x_r,0,\dots,0),$ 
 the diagonal invertible mapping
$K^l \rightarrow K^l$,
$(x_1,\dots,x_r)\mapsto (\delta_1 x_1,\dots,\delta_r x_r)$,
and the projections
$(x_1,\dots,x_{r+1})\mapsto (x_1,\dots,x_{r}),$
 $(x_1,\dots,x_{r+2})\mapsto (x_1,\dots,x_{r+1}),$
 $\dots,$
 $(x_1,\dots,x_{n})\mapsto (x_1,\dots,x_{n-1}).$
 Thus, thanks to Lemmas \ref{lem:DIimm} DI${}_{imm}$, \ref{lem:DIproj} DI${}_{proj}$ and \ref{lem:DIaut} DI${}_{aut}$, $\Delta (\Qc)$ is a polyhedron.
 One can note that it is only when applying the immersion as the last mapping in the composition chain that equalities are needed to define the last polyhedron.

@@

\begin{proof}
    Let $\PP$ be such polyhedron. We assume that $\PP \neq \emptyset$. By \ref{prop:carac} there exist a polydisc $D = \{x \in K^n : \val s_i x_i - b_i \ge 0, i=1,\ldots,n \}$ for some $s_1,\ldots,s_n, b_1,\ldots,b_n \in K ^n$ and an affine map $f : K^n \to K$ such that $\PP = f(D)$. Let $a_0,a_1,\ldots,a_n \in K$ such that $f(x) = a_0 + a_1 x_1 + \ldots + a_n x_n$. We can assume, without loss of generality, that the $a_i$'s are nonzero.

@@

\begin{theorem} \Cref{algo_LP} is correct.
\end{theorem}
\begin{proof}
  If the linear system $Dx=e$ has no solution, Problem \eqref{LP} is infeasible
  and \Cref{algo_LP} outputs the correct answer at step \ref{step:linear_empty}.
  Else, by \Cref{reducD} the input problem can be reduced to a new linear
  program with $D={\bf 0}$ and $e=0$, which is done at steps
  \ref{step:reducD:begin}-\ref{step:reducD:end},
  and the correct recursion is given at step \ref{step:reducD}.
  The reduction based on SNF from \Cref{solsLP} is performed at
  steps \ref{step:solsLP:begin}-\ref{step:solsLP:end} and the output
  at step \ref{step:solsLP} is correct.

@@

Recall that the \emph{Newton polygon} of a polynomial $P = \sum_{i=0}^{d} a_i T^i \in K[T]$ is
defined as the lower convex hull of the set $\{(i, \val a_i) \,|\, 0 \le i \le d\}$, {\it i.e.} the
graph of the greatest convex function $\PP : [0,d] \to \R$ such that $\PP(i) \leq \val a_i$
for $i=1,\ldots,d$. This function is piecewise affine and its slopes are exactly the opposites of the valuations
of the roots of $P$.

The following result shows that testing positive semidefiniteness of matrices over
valued fields reduces to checking whether the coefficients of $\chi_M$ are integral.

@@

As a consequence, matrices with integral coefficients are positive semidefinite.

@@

\begin{example}
  Let
  $$
  M = \begin{bmatrix} \frac{3}{5}+5 & \frac{4}{5} \\ \frac{4}{5} & -\frac{3}{5} \end{bmatrix}.
  $$
  The characteristic polynomial of $M$
  is $\chi_M = T^2-5T-4$. However when seen as a matrix over $K=\mathbb{Q}_5$, then $\chi_M \in \mathbb{Z}_5[T] = \OK[T]$. As such $M \in (\mathbb{Q}_5)^{2 \times 2}_+$, while nevertheless $M \not\in (\mathbb{Z}_5)^{2\times 2}$, and hence
  $(\mathbb{Q}_5)^{2 \times 2}_+ \not\subset (\mathbb{Z}_5)^{2 \times 2}$.
\end{example}

@@

In the real case, one often abuses the definition of spectrahedra, saying that the set
$\{x \in \mathbb{R}^n : A_0+\sum_{i=1}^n x_iA_i \succeq 0\}$ is also a spectrahedron.
Remark that this yields that every affine subset of $\mathbb{R}^n$ is also
a spectrahedron: indeed an affine equation $\ell(x) = 0$ is equivalent to the two inequalities
$\ell(x) \geq 0 \leq -\ell(x)$. Over a valued field it is necessary to give the following
definition in order to include affine sets in the family of spectrahedra.

@@

The class of spectrahedra in $K^{d \times d}$ (or in $K^n$) is closed under intersection: indeed one
has $(\mathcal{L}_1 \cap K^{d \times d}_+) \cap (\mathcal{L}_2 \cap K^{d \times d}_+) =
(\mathcal{L}_1 \cap \mathcal{L}_2) \cap K^{d \times d}_+$
, for two affine spaces
$\mathcal{L}_1 = A_0+\span{A_1,\ldots,A_n}$ and $\mathcal{L}_2 = A_0+\span{B_1,\ldots,B_n}$,
and
$(L_1 \cap \mathcal{S}_A) \cap (L_2 \cap S_B) = (L_1\cap L_2) \cap S_{\diag(A,B)}$ for
two affine spaces $L_1,L_2 \subset K^n$.
Moreover this class contains the polyhedra in $K^n$.

@@

\begin{definition}[Polyannulus]\label{def_annuli}
  A set of the form $\mathcal{C} = \{x \in K \,|\, a \le \val(x) \le b\}$, for $a,b \in \R^*_+$,
  is called an \emph{annulus}. A product $\mathcal{C}_1 \times \mathcal{C}_2 \times \cdots \times \mathcal{C}_n \subset K^n$,
  where each $C_i \subset K$ is an annulus, is called a \emph{polyannulus}.
\end{definition}

@@

\begin{theorem}
Polyannuli in $K^n$ are spectrahedral shadows with height $m=n$ and degree $d=4n$.
\end{theorem}
\begin{proof}
  Let $\mathcal{C} = \mathcal{C}_1 \times \cdots \times \mathcal{C}_n \subset K^n$ be as in \Cref{def_annuli},
  for some annuli $\mathcal{C}_1,\ldots,\mathcal{C}_n \subset K$. We claim that each $\mathcal{C}_i$ is a spectrahedral
  shadow of height $1$ and degree $4$. Assume $\mathcal{C}_i = \{x_i \in K : a_i \leq \val(x_i) \leq b_i\}$
  for some $a_i, b_i \in \R^*_+$ with $a_i < b_i$. Consider the spectrahedron
  $\mathcal{S}_{M^{(i)}} \subset K^2$ defined by
  $$
  \mathcal{S}_{M^{(i)}} = \left\{(x_i,y_i) \in K^2 :
  M^{(i)}(x_i,y_i) := \diag\left(\pi^{-a} x_i, \pi^{b} y_i,
  \begin{bmatrix}
    \pi^{-1} & -\pi^{-1} x_i  \\
    \pi^{-1} y_i & - \pi^{-1} \\
  \end{bmatrix}\right) \succeq 0
  \right\}.
  $$
  We claim that $x_i \in \mathcal{C}_i$ if and only if there exists $y_i \in K$ such that $(x_i,y_i) \in
  \mathcal{S}_{M^{(i)}}$.
  Indeed, by \Cref{caracsdp}, $M^{(i)}(x_i,y_i) \succeq 0$ if and only if $(x_i,y_i)$ is a solution of the system
  of inequalities:
  \begin{equation}
    \label[type]{eq:annulussyst}
    \begin{cases}
      \val(\pi^{-a} x_i) \ge 0 \\
  \val(\pi^{b} y_i) \ge 0\\
  \val(\pi^{-1}- \pi^{-1}) = +\infty \ge 0\\
  \val(\pi^{-2}\left( x_iy_i-1 \right))  \ge 0 
\end{cases}
\iff	
\begin{cases} 
  \val\left(x_i\right)\ge a\\
  \val\left(y_i\right)\ge -b\\
  \val\left(x_iy_i-1 \right) \ge 2
\end{cases}
\end{equation} 
  %Therefore, if $(x, y)$ verifies \eqref{eq:annulussyst} then $\val\left(x\right)\ge a$, $\val\left(y\right)\ge -b$ and $ \left( xy-1 \right) \ge 2$.
  The last inequality implies that $\val\left(x_i\right)+\val\left(y_i\right)=\val\left(x_iy_i\right) = \val\left(-1\right) =0$ and therefore that $\val\left(x_i\right)=-\val\left(y_i\right)\le -(-b) = b$, so $x_i \in \mathcal{C}_i$. 
Reciprocally if $x_i \in \mathcal{C}_i$ then $(x_i,x_i^{-1})$ is a solution of \eqref{eq:annulussyst}.
This proves our claim.
Finally, since $\mathcal{C} = \mathcal{C}_1 \times \cdots \times \mathcal{C}_n$, one has
\begin{equation*}
  \begin{aligned}
    \mathcal{C} &=
    \{x=(x_1,\ldots,x_n) \in K^n : \exists y = (y_1,\ldots,y_n) \in K^n, (x_i,y_i) \in
    \mathcal{S}_{M^{(i)}}, i=1,\ldots,n\} \\
    &= \{x \in K^n : \exists y \in K^n, (x,y) \in \mathcal{S}_M\}
  \end{aligned}
\end{equation*}
with $\mathcal{S}_M = \diag\left(M^{(1)}, M^{(2)}, \ldots, M^{(n)}\right) \in K[x,y]^{4n \times 4n}.$
\end{proof}

We conclude proving that, in general, annuli are not spectrahedra.
